\\Large The heat is on: Rising temperatures alter when, how, and where large terrestrial mammals move

### 2025-08-28 writing/appendix-b-gams.Rmd
re-knit appendix with updated figures

```{r pred-vs-pred-hrsfs, fig.cap="Hexplot of the fitted values from the HRSFs with and without including temperature."}
knitr::include_graphics('../figures/hrsf-with-without-temp-prediction-agreement.png')
```

```{r hrsf-se, fig.cap="Estimated standard error in the relative selection strength (RSS) for forest cover (\\%), elevation (km), and distance from water (km) as a function of temperature (see Fig. 3 in the main text). The grey contours indicate the extent of each speices' observed data. For ease of readability, the color bar values were capped to a maximum of 3 (original maximum was 7.00)."}
knitr::include_graphics('../figures/hrsf-surface-plots-se.png')
```

>>>>

```{r pred-vs-pred-hrsfs, fig.cap="Hexplot of the fitted values from the HRSFs with and without including temperature. For ease of visibility, values < -20 (0.41%) were set to -20."}
knitr::include_graphics('../figures/hrsf-with-without-temp-prediction-agreement.png')
```

```{r hrsf-se, fig.cap="Estimated standard error in the relative selection strength (RSS) for forest cover (\\%), elevation (km), and distance from water (km) as a function of temperature (see Fig. 3 in the main text). The black contours indicate the extent of each speices' observed data. For ease of readability, the color bar values were capped to a maximum of 3 (original maximum was 7.00)."}
knitr::include_graphics('../figures/hrsf-surface-plots-se.png')
```
